Object-based Auditory Scenes Similarity Retrieval and Classification With Wavelet Scattering

### 2016-07-11 paper/structureScene.tex
rephrase Section VI, paragraph 2

One should note that this quantization approach differs from unsupervised learning schemes such as the ones studied in \cite{bisot2016acoustic} that performs some variances estimates over the whole dataset and not solely on each scene, and reproject each scene in the resulting enhanced features space. Here, the aim of this process is to better balance the impact of salient events and texture like sounds on final decision by considering several ways of computing the similarity between scenes based on their centroids :

@@

The similarity between two centroids $c_i$ and $c_j$ is computed using a radial basis function (RBF) kernel $K^c$ combined with the local scaling method proposed in \cite{selfTuneManor2004}:
\begin{equation}
\label{eq:kc}
K^c_{ij} = exp\left( - \dfrac{\Vert c_i - c_j \Vert^2}{\Vert c_i - c_N \Vert \Vert c_j - c_N \Vert} \right) 
\end{equation}

where $c_N$ is the $N^{\mathrm{th}}$ nearest neihgbor of the centroid $c_i$, and $\Vert \cdot \Vert$ denotes the Euclidean norm.

>>>>

One should note that this quantization approach differs from unsupervised learning schemes such as the ones studied in \cite{bisot2016acoustic}, which performs some multivariate estimates over the whole dataset and not solely on each scene, and re-projects each scene in the resulting enhanced feature space.
Here, with the aim of balancing better the influence of salient events and texture-like sounds on the final decision, we consider several centroid-based similarity metrics between centroids:

@@

The similarity between two centroids $c_i$ and $c_j$ is computed using a radial basis function (RBF) kernel $K^c$ combined with the local scaling method proposed in \cite{selfTuneManor2004}:
\begin{equation}
\label{eq:kc}
K^c_{ij} = exp\left( - \dfrac{\Vert c_i - c_j \Vert^2}{\Vert c_i - c_N \Vert \Vert c_j - c_N \Vert} \right) 
\end{equation}
where $c_N$ is the $N^{\textrm{th}}$ nearest neighbor to the centroid $c_i$, and $\Vert \cdot \Vert$ denotes the Euclidean norm.
